Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
fix
fixed a few naiveties

We wrote our main control program, classify.py, so that it can choose either
Naive Bayes or Decision Trees classifier and any 
combination of  features. On top of this we wrote bash scripts that automated
looping through every combination of classifiers and features, along with
porting the results directly into the scorer.  Classify.py includes a help
switch -h, that explains the switches that control the different classifiers
and features along with any additional parameters that a certain feature might
support (for example, collocation has a window size parameter which defaults to
0) Performance was excellent for most of the features, allowing us to typically
run all of the words in the test set through every combination a classifier and
feature set in under an hour. (The number of runs can get quite high when you
factor in several parameters per feature, not just on/off)

@@

\subsubsection{Naive Bayes}

@@

Naive Bayes supported probability estimation, while the decision tree did not.

@@

\includegraphics[width=\textwidth]{pg_0001}
%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph

Collocation window of size 2--4 had the best performance, so we looked more closely at those.

\includegraphics[width=\textwidth]{pg_0002}

@@

\includegraphics[width=\textwidth]{pg_0003}

\includegraphics[width=\textwidth]{pg_0004}

@@

\begin{tabular}{l l | r r r}
& grain& precision& recall& attempted\\
\hline
\multirow{3}{*}{Naive Bayes} &
coarse  &  0.737 & 0.379 &   51.39\\
&mixed  &  0.730 & 0.375 &   51.39\\
& fine  &  0.693 & 0.356 &   51.39\\
\multirow{3}{*}{Decision Tree} &
coarse  &  0.612 & 0.612 &  100.00\\
&mixed  &  0.594 & 0.594 &  100.00\\
& fine  &  0.552 & 0.552 &  100.00\\
\end{tabular}

@@

\subsection{Looking through Different Corpora}

@@

The \naive Bayes and decision tree classifiers are not smart enough to sort out
a large number of features when the data sets are of small or moderate size,
which requires judicious choosing of features.  Co-occurrence, base word and
collocation with part of speech collocation seem to be more powerful features
than dependency parsing, and bootstrapping on the data in an attempt to get a
larger training base was ineffective because precision was too low.

>>>>

We wrote our main control program, classify.py, so that it can choose either
\Naive{} Bayes or Decision Trees classifier and any 
combination of  features. On top of this we wrote bash scripts that automated
looping through every combination of classifiers and features, along with
porting the results directly into the scorer.  Classify.py includes a help
switch -h, that explains the switches that control the different classifiers
and features along with any additional parameters that a certain feature might
support (for example, collocation has a window size parameter which defaults to
0) Performance was excellent for most of the features, allowing us to typically
run all of the words in the test set through every combination a classifier and
feature set in under an hour. (The number of runs can get quite high when you
factor in several parameters per feature, not just on/off)

@@

\subsubsection{\Naive{} Bayes}

@@

\Naive{} Bayes supported probability estimation, while the decision tree did not.

@@

\begin{figure}
\includegraphics[width=\textwidth]{baseline}
\caption{\label{fig:base}Baseline scores for our two baseline systems}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{pg_0001}
\caption{\label{fig1}}
\end{figure}

Collocation window of size 2--4 had the best performance (figure \ref{fig2}), so we looked more closely at those.

\begin{figure}
\includegraphics[width=\textwidth]{pg_0002}
%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph
\caption{\label{fig2}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}}
\end{figure}

@@

\begin{tabular}{l l | r r r}
& grain& precision& recall& attempted\\
\hline
\multirow{3}{*}{\Naive{} Bayes} &
coarse  &  0.737 & 0.379 &   51.39\\
&mixed  &  0.730 & 0.375 &   51.39\\
& fine  &  0.693 & 0.356 &   51.39\\
\multirow{3}{*}{Decision Tree} &
coarse  &  0.612 & 0.612 &  100.00\\
&mixed  &  0.594 & 0.594 &  100.00\\
& fine  &  0.552 & 0.552 &  100.00\\
\end{tabular}

@@

\subsubsection{Looking through Different Corpora}

@@

The \naive{} Bayes and decision tree classifiers are not smart enough to sort out
a large number of features when the data sets are of small or moderate size,
which requires judicious choosing of features.  Co-occurrence, base word and
collocation with part of speech collocation seem to be more powerful features
than dependency parsing, and bootstrapping on the data in an attempt to get a
larger training base was ineffective because precision was too low.
